### 2014-04-24 Response_to_R0_Reviews.tex

\textit{This manuscripts describes exciting work demonstrating the potential relevance
of acoustic radiation force impulse (ARFI) and B-Mode ultrasound for
delineating prostate zonal anatomy dimensions and volumes in application to
prostate cancer diagnosis and treatment.  The current state of the art involves
MRI imaging, but an ultrasound-based complement would offer the benefits of
being low-cost, real-time and portable.  This work should be of great interest
to both the technically and clinically oriented UI readership.  Overall, the
manuscript is very well written, and the presented in vivo, clinical data
support the conclusions drawn. There are a few minor questions/comments for the
authors to consider before publication, which is recommended:}

\begin{itemize}

    \item \textit{An artistic rendering or other illustration of prostate
            anatomy would facilitate the readers' understanding of the
            description of prostate anatomy in section II.A.}

    We agree with this suggestion, and we have added Figure 1 to the manuscript
    that outlines the McNeals zonal anatomy of the prostate in the coronal and
    sagittal views.

@@

    We have also emphasized that the imaging was performed endorectally by
    modifying the following statement in the same section:

    \textbf{3D volumetric imaging data was acquired endorectally\ldots}

    \item \textit{Why were the tracking beams focused (@ 60 mm) twice as deep
            as the pushing beams (@ 30 mm and above)?  It would seem that the
            radiation force would not propagate this far below the pushing
            focal position. (pg 6 lines 163 and 154, respectively).}

    The tracking beam transmit was focused at 60 mm to insonify a large lateral
    field of view and observe the off-axis shear wave propagation with the
    remaining 12 parallel receive beams that were not utilized in this work
    (lines 160-161). For each track beam, dynamic receive and receive aperture
    growth with a F/0.5 configuration were used to minimize the effect of the
    deep transmit focus.  Since only the ARFI imaging vectors were presented in
    this work--not the shear wave data--we have not amended the manuscript
    text to avoid confusing the reader with details not relevant to the data
    presented in this manuscript.

@@

    The following text has been added to Section III(C):

    \input{arfi_normalization}

    \item \textit{Pg 8 lines 205-214 describe that both B-Mode (for prostate
            capsule) and ARFI (for CG) data were used for segmentation.  First,
            how were these data combined?  Second, the use of B-Mode
            segmentation in addition to ARFI is not clearly specified in the
            titles, text and figures.  For example, in Table III, was the total
            volume calculation a result of both ARFI and B-Mode segmentations?
            In that case, the title and column labels describing "ARFI" total
            volume are confusing because they imply that the B-Mode
            segmentation data were not used.  The same is true for the other
            tables, figures, text, and the main Title of the manuscript.  If I
            understand correctly that B-Mode data were important to the overall
            total volume segmentation, then it would be appropriate to better
            clarify this point.  The point is currently confused by the main
            manuscript title, text and figures that generally refer to "ARFI"
            performance.  I believe the authors try to indicate that both
            B-Mode and ARFI data are used for the segmentation by referring to
            the "ultrasound" imaging performance, as in "… with a mean
            overestimation of of 16.82 ± 22.45\% by ultrasound imaging compared
            to MR volumes (Figure 6(b))." (pg 9 line 225), but this reader did
            not immediately appreciate that "ultrasound" referred to combined
            B-mode and ARFI segmentation as opposed to ARFI alone, and the
            "ARFI" labels throughout the rest of the text, tables, titles, and
            figures further confused this point.}

    This comment is greatly appreciated since the use of both B-mode and ARFI
    imaging for each segmentation was an important part of our methodology, and
    we (1) did not do enough to emphasize this point, and (2) confused matters
    by referring to `ARFI' exclusively in the results.  With respect to how the
    data were combined, we have added the following text to the manuscript
    (Section III(E.2)):

@@

    \input{bmode_arfi_coregistered}

    We also agree that our exclusive use of 'ARFI' for many of the tables,
    figures, manuscript title, and text was confusing, so we have updated all
    references to appropriate include B-mode when appropriate (not delineated
    here in the response due to the number of instances that were edited, but
    all manuscript changes are indicated in \textbf{bold} typeface).  The title
    of the manuscript has also been updated to reflect the importance of B-mode
    imaging in this process, and the abstract and conclusions have also been
    explicitly updated to include the fact that B-mode and ARFI imaging data
    were used in this study.

@@

    \item \textit{How many readers performed the B-Mode and ARFI segmentation
            per image? per entire study data set? Were the readers trained, and
            if so, how?  Did different readers segment the B-Mode and ARFI data
            sets?  Did the same radiologist who segmented the MRI images also
            segment the B-Mode and ARFI data?}

    All of the B-mode and ARFI images were segmented by two individuals (ZAM,
    TJG), and reviewed by a single, experienced ARFI imaging research (KRN).
    There was no formal training in reading the ARFI images since this work is
    our first effort to analyze our ability to evaluate our accuracy in
    identifying structures in ARFI prostate images.  The same individuals
    segmented both the B-mode images (for the capsules) and ARFI images (for
    the central glands).  All of the MR images were segmented by an experienced
    radiology fellow (CK) and reviewed by an experienced prostate radiologist
    (RG).  We have added the following text to the manuscript to delineate the
    readers / image segmenters for each part of the study (Section III(E.1)):

@@

    ARFI resolution within a native imaging frame is not considered a limiting
    factor in our ability to delineate the prostate central glands since the
    scan-conversion and slice decimation introduce resolution distortions that
    are at least an order-of-magnitude larger than our native image plane
    resolution.  ARFI image resolution would be a more realistic limiting
    factor if we were using those primary imaging frames for exclusive gland
    delineation, but our use of the 3 orthogonal planes for segmentation makes
    this resolution of higher-order parameter.  We have added to the following
    text to Section V to emphasize this point to the reader:

    \input{arfi_resolution}

    \item \textit{The authors explain that gross pathology weights and axis
            measurements were affected by the presence of peri-prostatic
            tissue.  Why could the peri-prostatic tissue not be differentiated
            from the prostatic tissue in histology after processing?  Wouldn't
            this enable better gold standard axis measurements?}

    We agree that very careful dissection of the gross organ from adjacent
    peri-prostatic tissue could be achieved, but to not disrupt the clinical
    pathologic processing of these samples, we could not specify specific
    pathology assistants to process these specimens, so there was some
    inherent variability associated with the time and effort that each
    assistant dedicated to removing this peri-prostatic tissue.  We felt that
    it was important to delineate this as a source of variability among our
    pathology specimens, though it is expected to be a higher-order source of
    error.

@@

    \item \textit{pg 12, line 329, change ``compliment'' to ``complement''.}

    Thank you for catching this grammatical error.  It actually existed in both
    the abstract and conclusion sections, and it has been corrected in both
    sections.

    \item \textit{Note that in my version of the manuscript, the figures and
            the captions written below them are blurry and difficult to read.
            This may just be a formatting issue with the automatic reviewer
            support system, but it is worth confirming that figures and their
            captions will be clear for publication.}

    High resolution images were uploaded for the review process, but their
    quality was definitely degraded during the rendering of the review PDF.  We
    will make sure that all images are properly reproduced at full resolution
    in new PDFs that are rendered of this manuscript.

@@

\textit{This is a nice study of ARFI imaging of the prostate that compares ARFI images
to MRI. Three areas of the paper could be improved:}

\begin{itemize}
    \item \textit{The ellipsoidal prostate volume estimate from pathology could be
        improved by using the prostate segmentation on each of the whole mount
        pathology slides to align the data to the MRI prostate surface. The
        volume comparison is further complicated by the shrinkage of the
        prostate after fixation.}

   Our ellipsoidal approximation of the prostate volume is a rough
   approximation from the surgical pathology reports, but we felt it was our
   best metric to approximate prostate size for the following reasons:

   \begin{itemize}
        \item The gross surgical pathology measurements used to make the
            ellipsoidal volume approximation were done after peri-prostatic
            tissue was dissected away, but before formalin fixation, avoiding
            the complication of tissue shrinkage associated with formalin
            fixation, which our pathologists estimated could be as much as 30\%
            of the prostate volume.
        \item Whole mount histology slides were explored for this purpose, but
            they suffer from post-fixation contraction, $\sim$ 3 mm slice
            thickness, and slice tearing and folding that compromise accurate
            cross-sectional area representations on a single slide.
            Additionally, the whole mount histology slides require some degree
            of image registration due to their arbitrary orientation on the
            slides, adding another source of error.
    \end{itemize}

@@

    \textbf{\input{path_volume_choice}}

    \item \textit{Image registration. The three orthogonal dimensions of the
            images do not mean much. The slice thickness in MRI causes
            significant errors along this measurement axis, while the
            lateral-to-lateral dimension in ARFI seems to be enlarged by the
            TRUS deformation (this is not mentioned in the discussion, but
            seems to be fairly obvious from Fig. 2 and 5, for example). A
            Jaccard index type of comparison would be preferable after rigid or
            possibly volume-preserving deformable registration.}

    We completely agree with the author that a more direct comparison of
    B-mode/ARFI imaging data with MR after ``unwrapping'' the deformation to
    register the images with one another would be more complete and satisfying,
    but two of the primary objectives of this work were (1) to compare prostate
    appearance and size in each native imaging, as would be seen by a clinician
    in each setting, and (2) to quantify the differences in the sizes of each
    dimension without the image registration to allow a clinician to
    cognitively register the images with known amounts of bias in each
    dimension.

    We are actively working on analyses that are focusing on comparing each
    imaging modality with whole mount histology as a gold standard, and then
    utilizing diffeomorphic image registration to spatially align each image
    for fused image guidance.  Both of these efforts require dedicated
    methodology description, and more importantly, method validation and
    error analysis that, in our opinions, warrant dedicated publications to be
    thoroughly presented to readers.

### 2014-04-24 fig_mcneal_anatomy.tex
spell-checked

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{figs/Mcneal_Zonal_Anatomy.jpg}
\caption{\textbf{Diagrams of McNeal’s zonal anatomy of the human
    prostate.~\cite{mcneal_path} It divides a human prostate into one
    nonglandular zone (the anterior fibromuscular stroma) and three glandular
    zones: central zone, peripheral zone and transition zone, denoted by CZ, PZ
    and TZ, respectively. (a) Coronal section of the prostate. V represents the
    verumontanum. (b) Sagittal section of the prostate. In the top part of the
    diagram, the seminar vesicles and ductus deferens enter the central zone
    and connect to the ejaculatory ducts, which merge with the urethra at the
    verumontanum. (Figure reprinted with permission.~\cite{Zhai2010a})}}
\label{fig:mcneal_anatomy} 
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.75\linewidth]{figs/Mcneal_Zonal_Anatomy.jpg}
\caption{\textbf{Diagrams of McNeal’s zonal anatomy of the human
    prostate.~\cite{mcneal_path} It divides a human prostate into one
    non-glandular zone (the anterior fibromuscular stroma) and three glandular
    zones: central zone, peripheral zone and transition zone, denoted by CZ, PZ
    and TZ, respectively. (a) Coronal section of the prostate. V represents the
    verumontanum. (b) Sagittal section of the prostate. In the top part of the
    diagram, the seminar vesicles and ductus deferens enter the central zone
    and connect to the ejaculatory ducts, which merge with the urethra at the
    verumontanum. (Figure reprinted with permission.~\cite{Zhai2010a})}}
\label{fig:mcneal_anatomy} 
\end{figure}
